### 2019-01-17 tex/manuscript.tex
critique
needs new narrative direction

	%title and author block
	{\title{Microstructure-derived strength in the acorn weevil exoskeleton}

@@

		Conversely, the endocuticle of Coleoptera appears to take advantage of this anisotropy to improve fracture resistance of the exoskeleton.
		Beetles in particular have a highly modified endocuticle comprised of large (5-20$\mu$m OD) unidirectional bundles of chitin, called macrofibers.
		Macrofibers are aligned in layers, as in Figs~INSERT-FIGS-HERE \cite{Kamp2010,Kamp2015}.
		Typically, endocuticle contains several layers of macrofibers, with the adjacent layers forming pairs. 
		The layers \emph{within} each pair are pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other, see Figs.~INSERT-REFS-HERE), while the stacking angle \emph{between} pairs is typically acute, although other configurations have been observed \cite{Hepburn1973,Kamp2010}.
		It is thought that this arrangement of the macrofibers contributes to the toughness of beetle exoskeletons by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

@@

@@

			These data have three important implications:
			\begin{enumerate}
				\item There is very little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology. 
				\item The endocuticle contributes more to the tensile strength of the rostrum than the exocuticle, possibly because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
				\item Thus, in addition to making the cuticle more flexible, the altered apical composite profile makes it less likely to break, suggesting a possible means by which the system evolved (via negative selection of breakage, maybe say this in conclusions).
			\end{enumerate}

			Finally, we observed that Young's modulus of elasticity is higher in specimens with a longer snout.
			This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) would need to be more flexible to avoid fracture during oviposition.
			Based on preliminary confocal microscopy data, we speculate that this phenomenon may be the result of a longer scrobe/transition/gradient from the basal profile to the apical profile in longer rostra.
			A decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.
			[OR SAY MORE CONCISELY THAT: based on prelim CLSM data we believe that the snout is reinforced against bucking with thicker exocuticle in the base of these species; as a result, the higher volume fraction of exocuticle in the snout increases young's modulus for such species]

@@

			From this pattern we hypothesize that the exocuticle-rich gular sutures are the most likely site for the initiation of void nucleation and failure of the integrated rostral cuticle in cross section.
			Structure failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
			We speculate that this could be the reason why the cross-sectional profile of \textit{C. caryae} is flattened ventrallyl
			Flattening this region may reduce tensile-strain across the gular sutures when the snout is bent dorsally, thus reducing the risk of fracture in the elongate, strongly-curved rostrum in this species.

@@

	\section{Conclusions} %shoot for 500 words

>>>>

	%title and author block
	{\title{Microstructure and mechanical behavior of the acorn weevil exoskeleton}

@@

		Conversely, the endocuticle of Coleoptera appears to take advantage of this anisotropy to improve fracture resistance of the exoskeleton.
		Beetles in particular have a highly modified endocuticle comprised of large (5-20$\mu$m OD) unidirectional bundles of chitin, called macrofibers.
		The macrofibers are strongly anisotropic, with an elastic modulus of ~8-9GPa along their longitudinal axis, but only 1-2 GPa along the transverse plane.
		Macrofibers are aligned in layers, as in Figs~INSERT-FIGS-HERE \cite{Kamp2010,Kamp2015}.
		Typically, endocuticle contains several layers of macrofibers, with the adjacent layers forming pairs. 
		The layers \emph{within} each pair are pseudo-orthogonal (i.e., angled approx. $90\degree$ to each other, see Figs.~INSERT-REFS-HERE), while the stacking angle \emph{between} pairs is typically acute, although other configurations have been observed \cite{Hepburn1973,Kamp2010}.
		It is thought that this arrangement of the macrofibers contributes to the toughness of beetle exoskeletons by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

@@

		We believe that each of these modifications contributes to the observed flexibility of the snout, but in different ways.
		Because the exocuticle is generally more rigid (and brittle) than the endocuticle due to its transverse isotropy and microstructure, a reduction in the relative thickness of this region would likely have the effect of increasing the flexibility of the resulting composite.
		Additionally, aligning the layers of endocuticle as a 45 deg cross ply would likely reduce the bending moment of the structure.
		The combined effect of these modifications is that the apex of the rostrum is able to bend until completely straight without fracture.

@@

			These data have three important implications:
			\begin{enumerate}
				\item There is very little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology. (singh 2016, jansen 2016)
				\item The endocuticle contributes more to the tensile strength of the rostrum than the exocuticle, possibly because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
				\item Thus, in addition to making the cuticle more flexible, the altered apical composite profile makes it less likely to break, suggesting a possible means by which the system evolved (via negative selection of breakage, maybe say this in conclusions).
			\end{enumerate}

			Finally, we observed that the elastic modulus is higher in specimens with a longer snout.
			This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) would need to be more flexible to avoid fracture during oviposition.
			Based on preliminary confocal microscopy data, we speculate that this phenomenon may be the result of a longer scrobe/transition/gradient from the basal profile to the apical profile in longer rostra.
			A decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.
			[OR SAY MORE CONCISELY THAT: based on prelim CLSM data we believe that the snout is reinforced against bucking with thicker exocuticle in the base of these species; as a result, the higher volume fraction of exocuticle in the snout increases young's modulus for such species]

@@

			From this pattern we hypothesize that the exocuticle-rich gular sutures are the most likely site for the initiation of void nucleation and failure of the integrated rostral cuticle in cross section.
			Structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
			We speculate that this could be the reason why the cross-sectional profile of \textit{C. caryae} is flattened ventrally
			Flattening this region may reduce tensile-strain across the gular sutures when the snout is bent dorsally, thus reducing the risk of fracture in the elongate, strongly-curved rostrum in this species.

@@

	\section{Conclusions} %shoot for 500 words
			Overall conclusion - the only difference between the flexible part and the stiff part is the microstructure; there is no difference in the mechanical behavior of the endocuticle at different locations on the snout and across species.
